### 2012-08-23 inst/examples/unmanaged_warning.Rmd
step by step: initial signals for #21

``` {r  simulate }
n <- 5000
x <- vector(mode="double", length=n)
a <- x
x[1] <- 8 # positive equilibrium
z <- rlnorm(n, 0, .1)
r = .75; k = 10; a[1]=1.55; H=1; Q = 3
for(t in 1:n){
  x[t+1] = z[t] *  x[t] * exp(r * (1 - x[t] / k) - a[t] * x[t] ^ (Q - 1) / (x[t] ^ Q + H ^ Q)) 
  a[t+1] = a[t] + .001
}
````

@@

``` {r modelbased}
A <- stability_model(dat, "OU")
B <- stability_model(dat, "LSN")
observed <- -2 * (logLik(A) - logLik(B))
m <- B$pars["m"]
````

>>>>

``` {r  simulate }
n <- 5000
x <- vector(mode="double", length=n)
a <- x
x[1] <- 8 # positive equilibrium
z <- rlnorm(n, 0, .1)
r = .75; k = 10; a[1]=1; H=1; Q = 3
for(t in 1:n){
  x[t+1] = z[t] *  x[t] * exp(r * (1 - x[t] / k) - a[t] * x[t] ^ (Q - 1) / (x[t] ^ Q + H ^ Q)) 
  a[t+1] = a[t] + 1/5000
}
````

@@

``` {r modelbased}
A <- stability_model(dat, "OU")
B <- stability_model(dat, "LSN")
observed <- -2 * (logLik(A) - logLik(B))
m <- B$pars["m"]

observed
m
````

Set up a parallel environment

``` {r parallel}
library(snow)
library(methods)
cl <- makeCluster(20, type = "MPI")
clusterEvalQ(cl, library(earlywarning))
```
